\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-04-06 Drafts and notes/Attempts/Old_draft_07.tex
Major change

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
    \def\svgwidth{\columnwidth}
    \import{./figs/}{#1.pdf_tex}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title[Rate of convergence]
{\textsc{Second-order state-constraint Hamilton-Jacobi equations}}
\thanks{The authors are supported in part by NSF grant DMS-1664424.}
\begin{abstract}
We investigate qualitatively the convergence of large, or state-constraint solution to nonlinear elliptic equation as the viscosity vanish.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Yuxi Han}
\address[Y. Han]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{yuxi.han@wisc.edu}
\author{Son N. T. Tu}
\address[S. N.T. Tu]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{thaison@math.wisc.edu}
\date{\today}
\keywords{first-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions.}
\subjclass[2010]{
35B40, %Asymptotic behavior of solutions, 
35D40, %Viscosity solutions
49J20, %Optimal control problems involving partial differential equations
49L25, %Viscosity solutions
70H20 %Hamilton-Jacobi equations
}
\maketitle
\setcounter{tocdepth}{1}
\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\subsection{Motivation} Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$. Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to 
\begin{equation}\label{eq:PDEeps}
    \begin{cases}
    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the (expectation) value function associated with a minimization of a stochastic optimal control problem with state-constraint. We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0$. Heuristically, the state-constraint second-order problem converges to the state-constraint first-order, which is associated with deterministic optimal control, which is described in the framework of viscosity solution as follows:
\begin{equation}\label{eq:PDE0}
    \begin{cases}
     \lambda u(x) + H(x,Du(x)) \leq 0\;\qquad\text{in}\;\Omega,\\
     \lambda u(x) + H(x,Du(x)) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
    \end{cases} \tag{PDE$_0$}
\end{equation}
Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all viscosity subsolution $v\in\rmC(\overline{\Omega})$. The problem is interesting since in the limit we no longer have blowing up behavior. In this paper, we are interested in the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0$. A boundary layer is expected to describe the behavior of this convergence near the boundary.
\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary in $\mathbb{R}^n$ and $H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian. 
\begin{itemize}
    \item[$\mathrm{(A1)}$] $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
\end{itemize}
We list the assumptions on a general Hamiltonian as follow.
\begin{itemize}
    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
    \begin{equation*}
        \begin{cases}
        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
    \end{equation*}
    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
\end{itemize}

@@

\noindent Let $\delta_0>0$ be a fixed number such that $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is of class $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$ (see \cite{gilbarg_elliptic_2001}), i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) \leq \delta_0$. We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that 
\begin{equation}\label{e:distance_def}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
    \end{cases}
\end{equation}
We recall that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Since $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is a viscosity solution to $|Du(x)|=1$ in $\Omega$. %we can assume that the extension $d(x)$ as also satisfies $|Dd(x)|\leq 1$ in $\Omega$. 
Let 
\begin{equation*}
    K_1 := \max_{x\in \overline{\Omega}} |\Delta d(x)| \qquad\text{and}\qquad K_2 := \max_{x\in \overline{\Omega}} |D d(x)|.
\end{equation*}
\noindent We denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the elliptic operator
\begin{equation*}
    \mathcal{L}^\varepsilon[u](x) := \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x), \qquad x\in \Omega.
\end{equation*}

@@

\begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u\in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$. Assume that $\lambda u(x)-f(x)\geq -K_0$ in $\Omega$, then for $\delta>0$ there exists $C_\delta = C(K_0,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that 
\begin{equation*}
    \sup_{x\in \overline{\Omega}_\delta} \Big(|u(x)|+|Du(x)|\Big) \leq C_\delta.
\end{equation*}
\end{thm}

\begin{proof} Let $\theta\in (0,1)$ be chosen later, $\varphi\in \mathrm{C}_c^\infty(\Omega)$, $0\leq \varphi\leq 1$, $\mathrm{supp}\;\varphi\subset \Omega$ and $\varphi = 1$ on $\Omega_\delta$ such that
\begin{equation}\label{e:ass_power}
    |\Delta \varphi(x)| \leq C|\varphi(x)|^\theta \qquad\text{and}\qquad |D \varphi(x)|^2 \leq C\varphi^{1+\theta}
\end{equation}
for $x\in \Omega$ and $C = C(\delta,\theta)$.
Let $w(x) = |Du(x)|^2$ for $x\in \Omega$, the goal is to derive an equation for $\varphi w$. The equation for $w$ is given by
\begin{equation*}
    -\varepsilon \Delta w + p|D u|^{p-2}D u \cdot D w + 2\lambda w - D f\cdot D u + \varepsilon |D^2u|^2 = 0 \qquad\text{in}\;\Omega.
\end{equation*}
Using that, we can derive an equation for $(\varphi w)$ as follows.
\begin{align*}
    &-\varepsilon \Delta (\varphi w) + p|D u|^{p-2}D u \cdot D (\varphi w) + 2\lambda (\varphi w) + \varepsilon \varphi|D^2u|^2 + 2\varepsilon \frac{D \varphi}{\varphi}\cdot D (\varphi w) \\
    &\qquad\qquad\qquad\qquad = \varphi(D f\cdot D u) + p|D u|^{p-2}(D u\cdot D \varphi)w -\varepsilon w \Delta \varphi + 2\varepsilon \frac{|D \varphi|^2}{\varphi}w
    \qquad\text{in}\;\mathrm{supp}\;\varphi.
\end{align*}
Assume that $\varphi w$ achieves its maximum over $\overline{\Omega}$ at $x_0\in \Omega$ then we can assume that $x_0\in \mathrm{supp}\;\varphi$, since otherwise the maximum of $\varphi w$ over $\overline{\Omega}$ is zero. By the classical maximum principle 
\begin{equation*}
    -\varepsilon \Delta(\varphi w)(x_0)\geq 0 \qquad\text{and}\qquad |D(\varphi w)(x_0)| = 0.
\end{equation*}
Using that in the equation of $\varphi w$ above, we obtain that
\begin{equation*}
    \varepsilon \varphi|D^2u|^2 \leq  \varphi (Df\cdot Du)+ p|Du|^{p-1} |D\varphi|w + \varepsilon w |\Delta\varphi|  + 2\varepsilon  w\frac{|D\varphi|^2}{\varphi},
\end{equation*}
where all terms are evaluated at $x_0$. Using \eqref{e:ass_power} we have
\begin{equation}\label{e:est_for_D^2u}
    \varepsilon \varphi|D^2u|^2 \leq  \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + C\varepsilon w \varphi^{\theta} + 2C\varepsilon  w\varphi^\theta.
\end{equation}
By Cauchy-Schwartz inquality, we have $n|D^2u|^2\geq (\Delta u)^2$, thus if $n\varepsilon < 1$ then
\begin{equation}\label{e:est_for_D^2u_2}
    \varepsilon |D^2u|^2 \geq \frac{(\varepsilon \Delta u)^2}{n\varepsilon} \geq (\varepsilon \Delta u)^2 = \left(\lambda u + |Du|^p - f\right)^2 \geq |Du|^{2p} - 2C_0|Du|^p \geq \frac{|Du|^{2p}}{2} - 2K_0.
\end{equation}
Using \eqref{e:est_for_D^2u_2} in \eqref{e:est_for_D^2u} we obtain that
\begin{equation*}
    \varphi\left(\frac{1}{2}w^p - 2K_0\right) \leq \varphi |Df|w^{\frac{1}{2}}+ Cp w^{\frac{p-1}{2}+1} \varphi^{\frac{1+\theta}{2}} + 3C\varepsilon w \varphi^{\theta}.
\end{equation*}
Multiply both sides by $\varphi^{p-1}$ we deduce that
\begin{align*}
    (\varphi w)^p \leq 4K_0\varphi^{p-1} + 2\Vert Df\Vert_{L^\infty}\varphi^p w^{\frac{1}{2}} + 2Cp \varphi^{\frac{2p+\theta - 1}{2}}w^{\frac{p+1}{2}} + 6C\varepsilon \varphi^{p+\theta - 1}w.
\end{align*}
Choose $2p+\theta -1 \geq p+1$, i.e., $p+\theta\geq 2$. This is always possible with the requirement $\theta \in (0,1)$, as $1<p <\infty$. We deduce that 
\begin{equation}\label{e:est_for_D^2u_3}
    (\varphi w)^p \leq C\left(1+ (\varphi w)^\frac{1}{2} + (\varphi w)^\frac{p+1}{2} +(\varphi w)\right)
\end{equation}
As a polynomial in $z = (\varphi w)(x_0)$, this implies that $(\varphi w)(x_0)\leq C$ where $C$ depends on coefficients of the right hand side of \eqref{e:est_for_D^2u_3}, which implies our desired gradient bound since $\overline{\Omega}_\delta\subset \mathrm{supp}\;\varphi$.
\end{proof}

@@

\begin{thm} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
\begin{equation*}
    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
\end{equation*}
where
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}}.
\end{equation*}
\end{thm}

\begin{proof}

\noindent To find a candidate for subsolution and supersolution to \eqref{eq:PDEeps}, we use the \emph{ansatz}
\begin{equation}\label{eq:ansatz}
    u(x) = C_\varepsilon d(x)^{-\alpha}, \qquad x\in \Omega
\end{equation}
as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$. Let us plug \eqref{eq:ansatz} into \eqref{eq:PDEeps} we obtain that 
\begin{align*}
    \lambda u(x) &\approx C_\varepsilon d(x)^{-\alpha},\\
    \frac{\partial u}{\partial x_i}(x) &\approx -\alpha C_\varepsilon d(x)^{-(\alpha+1)} \frac{\partial d}{\partial x_i}(x) \qquad\qquad\qquad \Longrightarrow\qquad |Du (x)|^p \approx \alpha^p C_\varepsilon^p d(x)^{-p(\alpha+1)}|D d(x)|^p,\\
    %\frac{\partial^2 u}{\partial x_i^2}(x) &\approx \alpha(\alpha+1)C_0 d(x)^{-(\alpha+2)}\left|\frac{\partial d}{\partial x_i}(x)\right|^2 -\alpha C_0 d(x)^{-(\alpha+1)}\frac{\partial ^2 d}{\partial x_i^2}(x),\\
    \varepsilon\Delta u(x) &\approx \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|D d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
\end{align*}
As $|D d(x)| = 1$ for $x$ near $\partial\Omega$, we see that as $x\to \partial \Omega$, the highest explosive order terms are
\begin{equation*}
        -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)} + C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}.
\end{equation*}
Setting them to zero, we deduce that
\begin{equation}\label{e:relation}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}} = \frac{1}{\alpha}(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+1}.
\end{equation}
We note that $\alpha+1 = \frac{1}{p-1}$ for convenience later. Recall that $_1 = \max_{\overline{\Omega}}|\Delta d(x)|$, let us denote
\begin{equation*}
    G = \left[\left(K_1\delta_0+(\alpha+1)\right)^{\alpha+1} - (\alpha+1)^{\alpha+1}\right]\alpha.
\end{equation*}

\begin{lem}\label{lem:subsln} For each $<\delta < \frac{1}{2}\delta_0$, if $\eta\geq G\varepsilon^{\alpha+1}$, we have

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
    \def\svgwidth{\columnwidth}
    \import{./figs/}{#1.pdf_tex}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title[Rate of convergence]
{\textsc{Second-order state-constraint Hamilton-Jacobi equations}}
\thanks{The authors are supported in part by NSF grant DMS-1664424.}
\begin{abstract}
We investigate qualitatively the convergence of large, or state-constraint solution to nonlinear elliptic equation as the viscosity vanishes.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Yuxi Han}
\address[Y. Han]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{yuxi.han@wisc.edu}
\author{Son N. T. Tu}
\address[S. N.T. Tu]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{thaison@math.wisc.edu}
\date{\today}
\keywords{first-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions.}
\subjclass[2010]{
35B40, %Asymptotic behavior of solutions, 
35D40, %Viscosity solutions
49J20, %Optimal control problems involving partial differential equations
49L25, %Viscosity solutions
70H20 %Hamilton-Jacobi equations
}
\maketitle
\setcounter{tocdepth}{1}
\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\subsection{Motivation} Let $\Omega$ be an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Let us consider the following Hamiltonian $ H(x,\varrho) = |\varrho|^p-f(x)$ for $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$. Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to 
\begin{equation}\label{eq:PDEeps}
    \lambda u^\varepsilon(x) + H(x,Du^\varepsilon(x)) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
    \end{cases} \tag{PDE$_\varepsilon$}
When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the (expectation) value function associated with a minimization of a stochastic optimal control problem with state-constraint. We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0$. Heuristically, the state-constraint second-order problem converges to the state-constraint first-order, which is associated with deterministic optimal control, which is described in the framework of viscosity solution as follows:
\begin{equation}\label{eq:PDE0}
     \lambda u(x) + H(x,Du(x)) \leq 0\;\qquad\text{in}\;\Omega,\\
     \lambda u(x) + H(x,Du(x)) \geq 0\;\qquad\text{on}\;\overline{\Omega}.
    \end{cases} \tag{PDE$_0$}
Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all viscosity subsolution $v\in\rmC(\overline{\Omega})$. The problem is interesting since in the limit we no longer have blowing up behavior. In this paper, we are interested in the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0$. A boundary layer is expected to describe the behavior of this convergence near the boundary.
\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary in $\mathbb{R}^n$ and $H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian. 
    \item[$\mathrm{(A1)}$] $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
    The following assumptions on $\Omega$ will also be used.
    \item[(A2)] There exists a universal pair of positive numbers $(r,h)$ and $\eta\in \mathrm{BUC}(\overline{\Omega};\mathbb{R}^n)$ such that $B(x+t\eta(x), rt)\subset\Omega$ for all $t\in (0,h]$.
    \item[(A3)] $\Omega$ is a bounded and star-shaped (with respect to the origin) open subset of $\mathbb{R}^n$ such that
        \mathrm{dist}(x,\overline{\Omega}) \geq \kappa r \qquad\text{for all}\; x\in (1+r) \partial\Omega, \;\text{for all}\;r>0,
for some $\kappa > 0$.
Assumption $\mathrm{(A1)}$ follows \cite{Lasry1989}, where the specific structure of the Hamiltonian enables more explicit estimates on the solution of \eqref{eq:PDEeps}. Assumptions $\mathrm{(A2)}$ or $\mathrm{(A3)}$ guarantees a comparison principle holds for the state-constraint problem \eqref{eq:PDE0}. We note that $\mathrm{(A1)}$ was first studied by M. Soner in \cite{Soner1986} (and $\mathrm{(A1)}$ holds for any smooth bounded domain), while $\mathrm{(A2)}$ was posed and studied by I. Capuzzo-Dolcetta and P. L. Lions in \cite{Capuzzo-Dolcetta1990}. We list the assumptions on a general Hamiltonian as follow.
    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.

@@

\noindent Let $\delta_0>0$ be a fixed number such that $x\mapsto \mathrm{dist}(x,\partial\Omega)$ is of class $\mathrm{C}^2$ on $\Omega\backslash \Omega_{\delta_0}$ (see \cite{gilbarg_elliptic_2001}), i.e., in the region where $0<\mathrm{dist}(x,\partial\Omega) \leq \delta_0$. We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that 
\begin{equation}\label{e:distance_def}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
    \end{cases}
\end{equation}
We recall that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Let 
\begin{equation*}
    K_1 := \max_{x\in \overline{\Omega}} |\Delta d(x)| \qquad\text{and}\qquad K_2 := \max_{x\in \overline{\Omega}} |D d(x)|.
\end{equation*}
\noindent We denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC^2(\Omega)$ the elliptic operator
\begin{equation*}
    \mathcal{L}^\varepsilon[u](x) := \lambda u(x) + H(x,Du(x)) - \varepsilon \Delta u(x), \qquad x\in \Omega.
\end{equation*}

@@

\begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u\in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u] = 0$ in $\Omega$. Assume that $\lambda u(x)-f(x)\geq -K_0$ in $\Omega$, then for $\delta>0$ there exists $C_\delta = C(K_0,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that 
\begin{equation*}
    \sup_{x\in \overline{\Omega}_\delta} \Big(|u(x)|+|Du(x)|\Big) \leq C_\delta.
\end{equation*}
\end{thm}
\noindent We provide a proof for this Theorem in Appendix for the reader's convenience.

@@

\begin{thm}\label{thm:wellposed1<p<2} If $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p< 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ then there exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that
\begin{equation*}
    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{\lambda} \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{\lambda} 
    \lim_{d(x)\to 0} u^\varepsilon(x) \,d(x)^\alpha = C_\varepsilon 
\end{equation*}
where
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^{\alpha+1}\right) \varepsilon^{\alpha+1}.
\end{equation*}
\end{thm}
\noindent This is Theorem I.1 in \cite{Lasry1989}. We provide a proof in Appendix with the explicit dependence of $C_\varepsilon$ in terms of $\varepsilon$ for later use, it is useful to note that $\alpha+1 = \frac{1}{p-1}$.

\subsection{Convergence result} We show the convergence (qualitatively) of \eqref{eq:PDEeps} to \eqref{eq:PDE0}. We first state the following Lemma (\cite{Capuzzo-Dolcetta1990}), which characterizes the state-constraint of the first-order equation
\begin{equation}\label{S_0}
 \lambda u(x) + H(x,Du(x)) = 0\;\qquad\text{in}\;\Omega. \tag{$S_0$}
\end{equation}

\begin{proof}[Proof of Theorem \ref{thm:qual}] By a priori estimate (Theorem \ref{thm:grad_1})
\begin{equation}\label{e:priorie_eps}
    |u^\varepsilon(x)| + |Du^\varepsilon(x)| \leq C_\delta \qquad\text{for}\;x\in \overline{\Omega}_\delta
\end{equation}
we deduce from the Arzel\'a--Ascoli theorem that there exists a subsequence $\varepsilon_j\to 0$ and a function $u^0\in \rmC(\Omega)$ such that $u^{\varepsilon_j}\to u^0$ locally uniformly in $\Omega$. By the stability of viscosity solution we easily deduce that 
\begin{equation}\label{eq:u0int}
   \lambda u^0(x) + H(x,Du^0(x)) = 0 \qquad\text{in}\;\Omega.
\end{equation}
Since $\lambda u^\varepsilon(x)\geq -C_2$ for all $x\in \Omega$, we also have $\lambda u^0(x)\geq -C_2$ for all $x\in \Omega$, thus together with \eqref{eq:u0int} we obtain $H(x,\xi) \leq C_2$ for all $\xi\in D^+u^0(x)$ and $x\in \Omega$. The coercivity $\mathrm{(H4)}$ implies that there exists $K>0$ such that 
\begin{equation*}
    |u^0(x) - u^0(y)| \leq K \qquad\text{for all}\;x,y\in \Omega.
\end{equation*}
Thus we can extend $u^0$ uniquely to $u^0\in \rmC(\overline{\Omega})$. We will use Lemma \ref{lem:max} to show that $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}$. It suffices to show that $u^0\geq w$ on $\overline{\Omega}$ where $w\in \rmC(\overline{\Omega})$ is the unique solution to \eqref{eq:PDE0}.

For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\partial \Omega) > \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity solution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, i.e., $v_\delta$ is the unique viscosity solution to
\begin{equation}\label{e:v_v}
    \begin{cases}
    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \leq 0 &\qquad\text{in}\;\Omega_\delta,\\
    \lambda v_\delta(x) + H(x,Dv_\delta(x)) \geq 0 &\qquad\text{on}\;\overline{\Omega}_\delta.
    \end{cases}
\end{equation}
As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ (see \cite{kim_state-constraint_2020}) and $w$ is bounded, therefore $\{v_\delta\}_{\delta>0}$ is uniformly bounded. Let $v^\varepsilon_\delta\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
\begin{equation}\label{eq:vv_eps}
\begin{cases}
    \lambda v_\delta^\varepsilon(x) + |Dv_\delta^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v_\delta^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
    \;\;\;\,\quad\qquad\qquad\qquad\qquad v_\delta^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
\end{cases}
\end{equation}
It is well-known that $v^\varepsilon_\delta\to v_\delta$ uniformly on $\overline{\Omega}_\delta$ as $\varepsilon\to 0$.

\subsection{Rate of convergence for first-order equation on nested domain}
For $\delta >0$, let $u\in \rmC(\overline{\Omega})$ and $u_\delta\in \rmC(\overline{\Omega}_\delta)$, respectively, be viscosity state-constraint solutions to 
\begin{equation*}
    \begin{cases}
    \lambda u(x)+H(x,Du(x)) \leq 0 \quad\text{in}\;\Omega,\\
    \lambda u(x)+H(x,Du(x)) \geq 0 \quad\text{on}\;\overline{\Omega},
    \end{cases}\qquad\text{and}\qquad 
    \begin{cases}
    \lambda u_\delta(x)+H(x,Du_\delta(x)) \leq 0 \quad\text{in}\;\Omega_\delta,\\
    \lambda u_\delta(x)+H(x,Du_\delta(x)) \geq 0 \quad\text{on}\;\overline{\Omega}_\delta.
    \end{cases}
\end{equation*} 
It is well-known that $0\leq u_\delta(x) - u(x) \leq C\delta$ for $x\in\overline{\Omega}_\delta$ and this rate is optimal. This can be proved easily by comparison principle when the domain have a scaling structure with $\mathrm{(A3)}$ holds, i.e., $\Omega_\delta = (1-\delta)\Omega$ (see \cite{kim_state-constraint_2020}). We have the following theorem for the general smooth domains.
